{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-01 bmvc_review.tex
Revised all most, all-the-way.

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
the embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy some criteria: minimal, manual intervention after
deployment and small footprint of computing resource consumption and
on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we slightly
modify the {\it E}nKCF to perform tracking in low frame rate videos dominated by large ego-motion.
large ego-motion.To verify the usefulness of the proposed method, we compared the performance of ours to those
of the existing online tracking methods. Experimental results showed
that the performance of ours are 72.53\% for precision on 20 pixels
and 52.90\% for success rate for OTB100 data, and 55.71\% and 41.71\%
for UAV123 data. These results confirmed that our method outperformed
the existing ones over 5\% on precision on 20 pixels and 10-20\% on
AUC on average. Our implementation ran at 340 fps for OTB100 and at
416 fps for UAV123 data that is faster than DCF (292 fps) for OTB100
and KCF (292 fps), DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

@@

@@

\begin{comment}\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

@@

\item We integrate the Particle Filter into the Multiple KCFs tracking
  as an additional filter that can avoid the drift due to one of the
  correlation filters we employ in our framework.

@@

In summary, the scale filter, $R_{s}$, handles the scale change providing more accurate
ROIs to $R_{t}^{L}$ and $R_{t}^{S}$. The translation filter, $R_{t}^{L}$, concentrates on a large search area to better recover from any potential drifts due to application of $R_{S}$ in previous frame. $R_{t}^{S}$, on the other hand, addresses the drawback of $R_{t}^{L}$ that it learns noisy shape features due to its large search area. Figure \ref{Workflow_figure_EnKCF} illustrates the workflow of the
proposed algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of
{\it E}nKCF. In the following section, we will briefly mention the theory behind the KCF.

@@

{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

{\it YoungWoo : What do you mean by this? Should we move it up before the EnKCF introduction? or Should we include more EnKCF-related text in it? I trimmed it further. I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}

@@

In this form, eq.~\ref{eq:FourierSolution} could prohibit us from implementing a
high speed object tracking as we need to perform large number of
element-wise division and multiplication operations. However, we know
from \cite{gray2006toeplitz} that all circulant matrices are
represented diagonally by the Fourier Transform regardless of the base
sample $x$.
%\begin{equation}
%X = Fdiag(\hat{x})F^{H},
%\label{eq:CirculantMatrixDFT}
%\end{equation}
%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
%Discrete Fourier Transform of the base sample $x$. 
%To simplify the
%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
%\begin{equation}
%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
%\label{eq:SimplificationX} 
%\end{equation}
Then, the optimized solution vector in the Fourier domain $\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
Similar to the diagonalization in the linear ridge regression
solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
ridge regression can be made diagonal using the same circulant matrix
theorem.  The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix}. In this study, we will only focus on
application of the Gaussian Kernel to the Correlation Filters. We
refer the readers to \cite{henriques2015high} for the detailed
documentation of the application of other kernels to the Correlation
Filters. The Gaussian kernelization is
expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

@@

\subsection{Particle Filter} \label{sc:PF}
The proposed {\it E}nKCF tracker does not update target's translation at every
$n=5$ frames due to application of a scale filter, $R_{s}$. To avoid this to perform 
smoother tracking, a Bayes Filter representing the evolution of target's motion can be added into our {\it E}nKCF tracking framework. To achieve this,
we consider a variant of a Bayes Filter, \textit{Particle Filter}. The Particle
Filter is a Sequential Monte Carlo method that uses a number of sample
points to represent the posterior probability density functions (pdf)
of the target motion.  The approximation becomes optimal with the
infinite number of particles, however, its run-time complexity grows
exponentially with the number of elements in the state space matrix,
$X_{t}$. As the focus of this study is to design a high speed tracker,
we keep the number of state space elements low and implement
computationally efficient \textit{Weight Function} and
\textit{Importance-Resampling} modules. We represent the state space
matrix as $X_{t} = \lbrace x,y,V_{x},V_{y}\rbrace$ where $x$ and $y$
are the centroid of the target and $V$ represents the velocity
components. We transit the particles with the first order Constant
Velocity model. The centroid components are applied Gaussian Noise
whereas the velocity components are assigned uniform noise
representative of most of the objects in our tests. The observation
likelihood is formulated based on the confidence map of $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$.  The weights for the particles are computed
as
\begin{equation}
	w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window in consideration in confidence map. We can also use
the euclidean distance of particles to the location of maximum response of 
the confidence map, however, we believe that this approach could result in drifts
in the case of multi-modal distributions.

The importance re-sampling module is triggered when the number of
effective particles is smaller than a pre-defined threshold to avoid
variance getting too small \cite{thrun2005probabilistic}. Re-sampling
is implemented with efficient low-variance ratio method
\cite{thrun2005probabilistic}. Finally, the expected mean of the
approximated posterior pdf is computed as $\hat{X}_{t} = \sum_{p=1}^{P}w_{p_{t}} X_{t}.$
The particles are assigned equal weight ($w_{p_{t}}=1/P$) after the importance
re-sampling step in approximating the posterior pdf. It should be
emphasized that we skip importance re-sampling step in the scale
filter operation as the scale filter contains \textit{target-only}
area and focuses on scale estimation. Additionally, it is
more likely to get noisy confidence map from $R_{s}$. Finally, at
every iteration we check the variance in the velocity components of
the particles to re-assign velocities from uniform initial
distribution to keep variance high enough.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran the proposed
{\it E}nKCF against two publicly, available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. 
OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects.

The UAVs employ mobiles platforms with limited computational resources. We
believe that the proposed high-speed tracker can better fit to tracking from
these platforms as it is highly efficient and scale adaptive. Taking into account these reasons, we first test it on UAV captured videos (UAV123). Later, we test in on OTB100 dataset which mostly contains videos captured from smart phones and cameras controlled by a human. Finally, the {\it E}nKCF2 is tested on temporally downsampled version of UAV123 dataset.

\textbf{Hyperparameter Selections.} Tuning the hyper-parameters of the
committee of the correlation filters are important as the each
correlation filter addresses the weakness of another one. For
instance, $R_{t}^{L}$'s main task is to recover from the previous
frame where only $R_{s}$ and particle filter's prior distribution are
used to estimate scale and translation. We set the learning rates
($\beta$) of $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ as $0.020$, $0.020$
and $0.010$. The desired response and hanning window for each KCF is
shown in fig.~\ref{fig:Filters}. Finally, the Gaussian kernel
parameter, $\alpha$ is tuned to $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. The learning rate is set to $0.12$
for $R_{t}^{L}$ as it is run in every frame for $E_{n}KCF2$.
In our particle filter implementation, we employ $1000$ particles and use the
\textit{efficient number of samples} metric shown below to determine
whether we need to perform importance re-sampling or not to keep
reasonable variance.

\textbf{Features Selections.} We use the fast Histogram of Oriented
Gradients (fHoG)\cite{felzenszwalb2010object} and
Color-naming\cite{van2009learning} features to learn target and
background models. $R_{t}^{L}$ uses both fHoG and color features as it
covers a large ROI where fHoG features may not be reliable alone. On
the other hand, $R_{t}^{S}$ is assigned only fHoG features as it
covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features
as it is assigned lower template size, yielding space to exploit two
feature modalities. We note that we use the same features for the {\it E}nKCF2 tracker.

@@

\textbf{Overall Performance on UAV123 Dataset.}
We compare the proposed tracker to other state-of-the-art high speed
trackers using the \textit{Precision} and \textit{Success\:Rate}
metrics. Precision is computed by thresholding the average euclidean
distance between the ground truth and tracking output over the frames
of one sequence. In precision, we rank the trackers based on the
precision numbers at 20 pixels. The success rate metric evaluates the
overlap between the ground truth and tracking output. The
intersection-to-union ratio of two regions over the frames of one
sequence. Finally, we count the number of frames with overlap larger
than the success rate threshold and divide it by the number of
frames. We compare our tracker to some other high-speed ($\geq$300
fps) state-of-the-art trackers including KCF\cite{henriques2015high},
CSK \cite{henriques2012exploiting}, STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset. The {\it E}nKCF tracker outperforms the other methods in
high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
the same dataset although it is $10$-$20$ times faster than these
trackers. On the other hand, the {\it E}nKCF does a decent job on
approximating the scale of the target in highly efficient manner. This
is proved by the fact that it ranks third best tracker in terms of
\textit{area under curve} (AUC) value for the success rate plot. It
outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
metric. Interestingly, it performs even better than most of the low
speed trackers. For instance, it outperforms Struct and DSST by $5\%$
and $10\%$ while running at more than $30$ and $10$ times larger
operation rate.

\textbf{Overall Performance on UAV123$\_$10fps Dataset.} We test our
slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps
version of the UAV123 dataset. The original dataset is already
dominated by fast object motion and large ego-motion. With
downsampling, it becomes very challenging with object and ego-motion
getting drastically larger. The performance of the proposed {\it
  E}nKCF2 tracker and other already mentioned trackers can be seen in
fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
high-speed correlation filter based trackers including KCF, DSST by
about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
$4$th in AUC and it is $20$-$30$ faster than the ones with
higher AUC.

@@

\textbf{Overall Performance on OTB100 Dataset.}
In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
OTB100 dataset to evaluate how good it generalizes to a traditional
object tracking dataset. Again, it performs slightly better than the
high speed trackers in precision. Interestingly, it outperforms the
another correlation filter based tracker, DSST while running only
$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
scale changes. It is ranked as the fifth best tracker while being the
second highest speed tracker behind MOSSE. It performs only around
$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
prove that {\it E}nKCF is not only a good candidate for tracking on a
UAV-based mobile platform but also mobile platforms on smart phones.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems. This is primarily because most of
embedded systems already includes image acquisition pipeline and a
tremendous amount of progresses on research has been made for many
areas in computer vision. However, to successfully deploy a computer
vision algorithm on any existing embedded systems, a vision algorithm
needs to satisfy, at least, two criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and on executable code, with the assumption of reasonably good
performance. To this end, in this paper, we propose an ensemble of the
kernelized correlation filters (KCF), we call {\it E}nKCF, for a
single-target object tracking. In particular, we developed a committee
of KCFs to specifically address the scale-change and dynamic maneuver
of the target over frames. In addition, we devised a Bayes filter for
a smooth transition between individual KCFs' executions. Also, we
slightly modify the {\it E}nKCF to perform tracking in low frame rate
videos dominated by large ego-motion.  large ego-motion.  To verify
the usefulness of the proposed method, we compared the performance of
ours to those of the existing online tracking methods. Experimental
results showed that the performance of ours are 72.53\% for precision
on 20 pixels and 52.90\% for success rate for OTB100 data, and 55.71\%
and 41.71\% for UAV123 data. These results confirmed that our method
outperformed the existing ones over 5\% on precision on 20 pixels and
10-20\% on AUC on average. Our implementation ran at 340 fps for
OTB100 and at 416 fps for UAV123 data that is faster than DCF (292
fps) for OTB100 and KCF (292 fps), DCF (457 fps), and STC (350 fps)
for UAV123.
\end{abstract}

@@

\begin{figure*}[!t]
\includegraphics[width=\textwidth]{figures/ResultsIntroduction.pdf}
\caption{Some results of the proposed high-speed ($\geq300$fps) {\it E}nKCF tracker on UAV123 dataset where scale change between the frame in the top row and bottom row is large or small($\leq0.5$, or $\geq2$).}
\label{Workflow_figure_EnKCF}
\end{figure*}

@@

\begin{comment}

\item \textbf{Re-Detection} A target loss is inevitable in object
  tracking. To cope with this, we developed a new target, re-detection
  that reliably detects when to lose the target and effectively
  re-detect the lost target. {\it How we can show how good our
    re-detection method is?}

@@

@@

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. A translation
filter, $R_{t}^{L}$, is intended to look at a larger search area to
estimate the target's translation and recover from any potential
drifts. Another translation filter, $R_{t}^{S}$, on the other hand, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. Figure
\ref{Workflow_figure_EnKCF} illustrates the workflow of the proposed
algorithm and alg.\ref{alg:MKCF} shows the pseudo-code of {\it
  E}nKCF. In the following section, we will briefly mention the theory
behind the KCF.

@@

\begin{comment}
{\it Burak: The KCF section doesn't fit the section before and
  after. In addition, it's still too long.}

{\it YoungWoo : What do you mean by this? Should we move it up before the EnKCF introduction? or Should we include more EnKCF-related text in it? I trimmed it further. I wanted to keep some equations because they include hyper-paramaters that is important for EnKCF.}
\end{comment}

@@

In this form, the equation \ref{eq:FourierSolution} could prohibit us
from implementing a high speed object tracking as we need to perform
large number of element-wise division and multiplication
operations. However, we know from \cite{gray2006toeplitz} that all
circulant matrices are represented diagonally by the Fourier Transform
regardless of the base sample $x$.
%\begin{equation}
%X = Fdiag(\hat{x})F^{H},
%\label{eq:CirculantMatrixDFT}
%\end{equation}
%where $F$ denotes a constant Fourier Transform matrix and $x$ is the
%Discrete Fourier Transform of the base sample $x$. 
%To simplify the
%cost function formulation in eq.~\ref{eq:FourierSolution} we multiply
%$X$ in eq.~\ref{eq:CirculantMatrixDFT} with $X^{H}$ yielding
%\begin{equation}
%X^{H}X = Fdiag(\hat{x}^{*}\odot \hat{x})F^{H}.
%\label{eq:SimplificationX} 
%\end{equation}
Then, the optimized solution vector in the Fourier domain $\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
Similar to the diagonalization in the linear ridge regression
solution in eq.~\ref{eq:DiagonalizedPrimalSolution}, the kernelized
ridge regression can be made diagonal using the same circulant matrix
theorem.  The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix}. In this study, we will only focus on
application of the Gaussian Kernel to the Correlation Filters. We
refer the readers to \cite{henriques2015high} for the detailed
documentation of the application of other kernels to the Correlation
Filters. The Gaussian kernelization is
expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. The
multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

@@

\subsection{Particle Filter for Smoothing Transition of KCFs} \label{sc:PF}
As explained earlier, the {\it E}nKCF upates a target's translation at
every other $k$ frames, particularly for estimating the target's
scale. Although the strategy of updating every other $k$th frames will
result in an optimal run-time performance, this may lead any potential
drifts at the later frames. To prevent such potential mishaps from
happening, we developed a Bayes filter that incorporates a target's
motion to smooth any outputs from the {\it E}nKCF. In particular, we
use a particle filter to estimate the target's image coordinate based
on the {\it E}nKCF's outputs. A particle filter is a sequential Monte
Carlo method that uses a finite number of particles or samples to
estimate the posterior probability density of a state of the system
\cite{thrun2005probabilistic}. In this study, the state represents a
target's pixel coordinates and its motion. In particular, the state of
the particle filter, $X_t$, is represented by $\lbrace x, y, v_{x},
v_{y} \rbrace$, where $x$ and $y$ are the pixel coordinates of the
target's centroid, $v_x$ and $v_y$ are the estimated velocity along
the $x$-axis and $y$-axis. The particle filter predicts, using a
constant velocity motion model, a target's state by generating a
predefined number of particles. And then the particle filter uses the
confidence maps of {\it E}nKCF as observation to update the state. The
weight of a particle is computed as:
\begin{equation}
w_{p_{t}}(x_{t},y_{t}) = \sum_{i=1}^{N}\sum_{j=1}^{N} y_{R}(x_{t}-i,y_{t}-j)
\end{equation}
where $w_{p}$ denotes the weight of the particle $p$ at time $t$ and
$N$ denotes the size of the window as that of a confidence
map. Alternatively one can also use the euclidean distance of
particles to the location of maximum response of the confidence
map. This alternative, however, would result in drifts.

We chooses some particles based on their importance to estimate the
target's next state, i.e., its pixel coordinates as $\hat{X}_{t} =
\sum_{p=1}^{P}w_{p_{t}} X_{t}.$ Note that, unlike a typical operation
of a particle filter, we skip the importance re-sampling step when the
scale filter, $R_{s}$, estimates the target's scale change. This is
because we observe the confidence map from the scale filter, $R_s$ is
sometime noisy. In addition, at every iteration, we check the variance
in the velocity components of the particles to re-assign velocities
from uniform initial distribution to keep variance high enough.

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we choose two public,
available datasets:
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}}
and
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
The OTB100 dataset is comprised of the videos about 100 objects
whereas UAV123 dataset contains aerial footage of 123 objects. We aims
at developing an object tracking algorithm that ``efficiently'' runs
in ``high speed,'' $\ge 300$ fps. Given this goal, we believe that the
UAV123 video data is a better fit in evaluating the performance of the
proposed algorithm. This is because there are many challenging scenes,
e.g., abrupt scale/illumination changes as all the targets were
recorded from bird-eye view. Although we are primarily interested in
developing an algorithm for mobile, embedded robotic applications, it
is important to compare the performance of the proposed algorithm with
those of the state-of-the-art in nominal dataset for comparison. To
this end, we chose the OTB100 data that contains the videos recorded
from smart phones and typical cameras in perspective view.

{\it Burak: What does this mean?}  Finally, the {\it E}nKCF2 is tested
on temporally downsampled version of UAV123 dataset.

\textbf{Finding Optimal Hyperparameters} Each of three KCFs in {\it
  E}nKCF is designed for addressing a specific challenge of a single,
target tracking problem. Thus each of them should have different value
for the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$.

{\it Burak: This is a dangling sentence.} The desired response and
hanning window for each KCF is shown in fig.~\ref{fig:Filters}.

For the kernel of the Gaussian neighboring function, we empirically
found the optimal values of $\alpha$ as $0.6$, $0.4$, and $0.4$ for
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$, and the learning rate as $0.12$
for $R_{t}^{L}$.

{\it Burak: Did we even mention whether $R_{t}^{L}$ runs on every
  frame? This might confuse others because all I remembered is we use
  each of KCFs at every other $k$ or $n$ frames.}

For the particle filter implementation, we found $1000$ is the optimal
number of particles,

{\it Burak: ?}
and use the \textit{efficient number of samples}
metric shown below to determine whether we need to perform importance
re-sampling or not to keep reasonable variance.

\textbf{Features Selections.} We used the fast Histogram of Oriented
Gradients (fHoG)\cite{felzenszwalb2010object} and
color-naming\cite{van2009learning} features to learn target and
background models. $R_{t}^{L}$ uses both fHoG and color features as it
covers a large ROI where fHoG features may not be reliable alone. On
the other hand, $R_{t}^{S}$ is assigned only fHoG features as it
covers smaller ROI. Finally, $R_{s}$ uses both fHoG and color features
as it is assigned lower template size, yielding space to exploit two
feature modalities. We note that we use the same features for the {\it
  E}nKCF2 tracker.

@@

\textbf{Performance on UAV123 Dataset.}  We compared the performance
of the proposed tracking algorithm with those of the state-of-the-art
high speed tracking algorithms in the \textit{Precision} and
\textit{Success\:Rate} metrics. Precision is computed by thresholding
the average euclidean distance between the centroid of the ground
truth and that of an tracking algorithm output.

{\it YoungWoo: End of 04/30/17}

In precision, we rank the trackers based on the precision numbers at
20 pixels. The success rate metric evaluates the overlap between the
ground truth and tracking output. The intersection-to-union ratio of
two regions over the frames of one sequence. Finally, we count the
number of frames with overlap larger than the success rate threshold
and divide it by the number of frames. We compare our tracker to some
other high-speed ($\geq$300 fps) state-of-the-art trackers including
KCF\cite{henriques2015high}, CSK \cite{henriques2012exploiting},
STC\cite{zhang2014fast},
MOSSE\cite{bolme2010visual,henriques2015high}. Also, some relatively
lower-speed ($\geq$50) trackers are used to evaluate the robustness of
the proposed trackers. These trackers include SAMF\cite{li2014scale},
DSST\cite{danelljan2014accurate}, LCT\cite{ma2015long},
MEEM\cite{zhang2014meem} and Struck\cite{hare2012efficient}.
Fig.~\ref{fig:UAV123_DATASET} shows the results on the UAV123
dataset. The {\it E}nKCF tracker outperforms the other methods in
high-speed trackers category by $3\%$-$15\%$ at 20 pixels precision
accuracy whereas it is only $5\%$ worse than SAMF, DSST and Struck on
the same dataset although it is $10$-$20$ times faster than these
trackers. On the other hand, the {\it E}nKCF does a decent job on
approximating the scale of the target in highly efficient manner. This
is proved by the fact that it ranks third best tracker in terms of
\textit{area under curve} (AUC) value for the success rate plot. It
outperforms the high speed trackers by about $20\%$-$25\%$ in AUC
metric. Interestingly, it performs even better than most of the low
speed trackers. For instance, it outperforms Struct and DSST by $5\%$
and $10\%$ while running at more than $30$ and $10$ times larger
operation rate.

\textbf{Performance on UAV123$\_$10fps Dataset.} We test our
slightly modified version of the {\it E}nKCF, {\it E}nKCF2, on the
UAV123$\_$10fps dataset. This dataset is downsampled at $10$ fps
version of the UAV123 dataset. The original dataset is already
dominated by fast object motion and large ego-motion. With
downsampling, it becomes very challenging with object and ego-motion
getting drastically larger. The performance of the proposed {\it
  E}nKCF2 tracker and other already mentioned trackers can be seen in
fig.~\ref{fig:UAV123_10fpsDATASET}. Our tracker outperforms other
high-speed correlation filter based trackers including KCF, DSST by
about $15\%$-$20\%$ whereas having similar precision rate to SAMF. On
the other hand, it does decent job in scale estimation. It ranks as
$4$th in AUC and it is $20$-$30$ faster than the ones with
higher AUC.

@@

\textbf{Performance on OTB100 Dataset.}
In addition to UAV123 dataset, we test the {\it E}nKCF tracker on the
OTB100 dataset to evaluate how good it generalizes to a traditional
object tracking dataset. Again, it performs slightly better than the
high speed trackers in precision. Interestingly, it outperforms the
another correlation filter based tracker, DSST while running only
$5\%$ behind of another low-speed scale adaptive SAMF tracker. As in
UAV123 dataset, the {\it E}nKCF performs exceptionally in handling the
scale changes. It is ranked as the fifth best tracker while being the
second highest speed tracker behind MOSSE. It performs only around
$2\%$ worse than SAMF and MEEM trackers in terms of AUC. These numbers
prove that {\it E}nKCF is not only a good candidate for tracking on a
UAV-based mobile platform but also mobile platforms on smart phones.
